Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-10-22 text/sparks.tex
Edits to spark lines table

\caption{Example population dynamic black swans from the Global Population
  Dynamics Database and descriptions of their causes. Red and blue dots
  indicate downward and upward events that have a probability of occurring of
  0.001\% or less if the population dynamics were explained by a Gompertz model
  with normally distributed process noise. These populations are a non-random
  sample that we were able to verify in the primary literature.}\\

@@

\includegraphics[width=2cm]{../analysis/sparks/20579} &
Grey heron,
\textit{Ardea cinerea},
UK &
Severe winters in 1929, 1940--1942, and 1962--1963; 1963 event so severe that
recovery took three times as long as expected &
\citep{stafford1971} \\

>>>>

\caption{Example population dynamic black swans from the Global Population
  Dynamics Database and a description of their causes. Red and blue dots
  indicate downward and upward events that have a 0.001\% probability or less of
  occurring if the population dynamics were explained by a Gompertz model
  with normally distributed process noise. These populations are a non-random
  sample that we verified in the primary literature.}\\

@@

\includegraphics[width=2cm]{../analysis/sparks/20579} &
Grey heron,
\textit{Ardea cinerea},
UK &
Severe winters in 1929, 1940--1942, and 1962--1963; 1963 event so severe that
recovery took three times loner than expected &
\citep{stafford1971} \\
